### 2024-11-25 paper/al.tex
Fix 5.2 and 5.3

\begin{figure}[h]
  \centerline{\includegraphics[width=15cm]{fig/return}}
  \caption[\texttt{return} instruction]{\texttt{return} instruction}
    \label{fig:return}
  \centerline{\includegraphics[width=15cm]{fig/if}}
  \caption[\texttt{if} instruction]{\texttt{if} instruction}
    \label{fig:if}
\end{figure}

@@

% TODO: Clever way to distinguish jargon rather then \textit
% Formal model
To formally specify the prose specification, we construct a formal model to
describe Wasm control flow.
% Execute
Rather than relying on a program counter, we employ an instruction stack to
represent execution progress.
Execution proceeds by popping an instruction from the stack and performing its
operation.
To avoid confusion with the stack that contains values interleaved with
contexts, we refer to the latter as the \textit{interleaved stack}.
This approach allows us to define the \textit{execute} operation without
introducing a program counter.

% Jump
We then split two distinct usages of the \textit{jump} operation:
\textit{enter} and \textit{exit}.
Since Wasm supports structured control flow, the \textit{jump} operation is
used either for entering or exiting control structures such as a function body
and a block of instructions.
% Enter
We define the \textit{enter} as the operation of pushing the context associated
with the jump onto the interleaved stack and the instructions within
the structure onto the instruction stack.
On the contrary, we define \textit{exit} as the operation of popping the
corresponding context and instructions.

% State transition
To express the \textit{enter} and \textit{exit} operation formally, we model
them as state transitions.
We define a Wasm state as a tuple of the interleaved stack, the instruction
stack, and the store.
For brevity, we omit the store in this discussion.
Let the interleaved stack initially contains $n$ entries $we_1 ~ ... ~ we_n$,
and the instruction stack contains $m$ entries $wi_1 ~ ... ~ wi_m$.
Suppose $wi_1$ is a control instruction that enters a control structure
containing a sequence of k instrucitons $wi_{11} ~ ... ~ wi_{1k}$ with an
associated context $wc$.
The \textit{enter} operation can be expressed as the following state transition:
\[
(we_1 ~ ... ~ we_n, ~ wi_1 ~ ... ~ wi_m) \quad\leadsto\quad
  (
    wc ~ we_1 ~ ...  ~ we_n, ~
    wi_{11} ~ ... ~ wi_{1k} ~ \textbf{end}_{wc} ~ wi_2 ~ ... ~ wi_m
  )
\]

% TODO: Fix end instruction in the 5.3

% End
Note that we introduce an administrative instruction, \textbf{end}, to mark the
end of the structure in the instruction stack.
The prose specification describes a behavior that must take place when the end
of a structure is reached without control transfer.
\cref{fig:exiting-label} illustrates this behavior for a function.
While not a Wasm instruction itself, it is presented in the same format as Wasm
instructions.
Therefore, we formalize this behavior as an administrative instruction,
\textbf{end}.

\begin{figure}[h]
  \centerline{\includegraphics[width=15cm]{fig/returning}}
  \caption[Behavior for the end a block]{Behavior for the end of a block}
    \label{fig:exiting-label}
\end{figure}

Similarly, the \textit{exit} operation can be described as a transition of Wasm
state.
Suppose $wi_1$ is a control instruction that exits a control structure, and $i$
values $wv_1 ~ ... wv_i$ are at the top of the interleaved stack, followed by a
context $wc$, and $j$ instructions $wi_1 ~ ... ~ wi_j$ are at the top of the
instruction stack followed by an \textbf{end} instruction.
The \textit{exit} operation can be represented as the following state transition:
\[
(wv_1 ~ ... ~ wv_i ~ wc ~ we_{i+2} ~ ...  ~ we_n,
  wi_1 ~ ... ~ wi_j ~ \textbf{end}_{wc} ~ wi_{j+2} ~ ..  ~ wi_m)
  \quad\leadsto\quad
  (we_{i+1} ~ ... ~ we_n, wi_{j+1} ~ ... ~ wi_m)
\]
This transition model provides the foundation for the formal definition of AL.

@@

{
\renewcommand{\arraystretch}{0.8835}  % Decrease row spacing locally
\begin{align*}
\begin{array}{lcccrlr}
%
% Algorithm
  \text{Algorithm}\quad& A &\ni& a &::=& ~ \rel ~ (s, \seq e, \seq i) ~ | ~ \fun ~ (s, \seq e, \seq i) \\
%
% Instruction
  \text{Instruction}\quad& I &\ni& i &::=& ~ \ifi ~ (e, \seq i, \seq i) &\quad\text{(If)} \\
    &&&& | & ~ \eitheri ~ (\seq i, \seq i) &\quad\text{(Either)} \\
    &&&& | & ~ \enteri ~ (e, e) &\quad\text{(Enter)} \\
    &&&& | & ~ \pushctxi ~ e &\quad\text{(Push Context)} \\
    &&&& | & ~ \pushi ~ e &\quad\text{(Push)} \\
    &&&& | & ~ \popctxi ~ e &\quad\text{(Pop Context)} \\
    &&&& | & ~ \popi ~ e &\quad\text{(Pop)} \\
    &&&& | & ~ \popni ~ (e, e) &\quad\text{(Pop N)} \\
    &&&& | & ~ \popalli ~ e &\quad\text{(Pop All)} \\
    &&&& | & ~ \leti ~ (e, e) &\quad\text{(Let)} \\
    &&&& | & ~ \trapi &\quad\text{(Trap)} \\
    &&&& | & ~ \returnreli &\quad\text{(Return Relation)} \\
    &&&& | & ~ \returnfuni ~ e &\quad\text{(Return Function)} \\
    &&&& | & ~ \executei ~ e &\quad\text{(Execute)} \\
    &&&& | & ~ \calli ~ (s, s, \seq{e}) &\quad\text{(Let Call)} \\
    &&&& | & ~ \replaceframei ~ (p^+, e) &\quad\text{(Replace Frame)} \\
    &&&& | & ~ \replacestorei ~ (p^+, e) &\quad\text{(Replace Store)} \\
%
% Expression
  \text{Expression}\quad& E &\ni& e &::=& ~ \vare ~ s &\quad\text{(Variable)} \\
    &&&& | & ~ \nume ~ n &\quad\text{(Number)} \\
    &&&& | & ~ \boole ~ b &\quad\text{(Boolean)} \\
    &&&& | & ~ \fnamee ~ s &\quad\text{(Function Name)} \\
    &&&& | & ~ \liste ~ \seq e &\quad\text{(List)} \\
    &&&& | & ~ \stre ~ \seq{(s, e)} &\quad\text{(Record)} \\
    &&&& | & ~ \tupe ~ \seq e &\quad\text{(Tuple)} \\
    &&&& | & ~ \casee ~ (s, \seq e) &\quad\text{(Tagged Tuple)} \\
    &&&& | & ~ \une ~ (unop, e) &\quad\text{(Unary Operation)} \\
    &&&& | & ~ \bine ~ (binop, e, e) &\quad\text{(Binary Operation)} \\
    &&&& | & ~ \acce ~ (e, p) &\quad\text{(Access)} \\
    &&&& | & ~ \upde ~ (e, p^+, e) &\quad\text{(Update)} \\
    &&&& | & ~ \cate ~ (e, e) &\quad\text{(Concatenation)} \\
    &&&& | & ~ \compe ~ (e, e) &\quad\text{(Composition)} \\
    &&&& | & ~ \meme ~ (e, e) &\quad\text{(Membership)} \\
    &&&& | & ~ \choosee ~ e &\quad\text{(Choose)} \\
    &&&& | & ~ \lene ~ e &\quad\text{(Length)} \\
    &&&& | & ~ \iscaseofe ~ (e, s) &\quad\text{(Check Tag)} \\
    &&&& | & ~ \getcurctxe  &\quad\text{(Get Current Context)} \\
    &&&& | & ~ \ctxkinde ~ s &\quad\text{(Context Kind)} \\
    &&&& | & ~ \itere ~ (e, iter, \seq{s}) &\quad\text{(Iteration)} \\
    &&&& | & ~ \matche ~ (e, e) &\quad\text{(Match)} \\
    &&&& | & ~ \hastypee ~ (e, s) &\quad\text{(Has Type)} \\
\end{array}
\end{align*}
}

@@

% algorithm
An algorithm is either an AL relation or an AL function, corresponding to the
relation and the function definitions in the DSL.
% instruction
An AL instruction is \ifi{} for conditionally choosing a branch, \eitheri{} for
nondeterministically choosing a branch, \enteri{} for entering a block,
\pushctxi{} for pushing a Wasm context, \pushi{} for pushing a Wasm value,
\popctxi{} for popping a Wasm context, \popi{} for popping a Wasm value,
\popni{} for popping $n$ Wasm values, \popalli{} for popping all Wasm values
within a Wasm context, \leti{} for let binding, \trapi{} for trapping,
\returnreli{} for returning from an AL relation, \returnfuni{} for returning
from an AL function, \executei{} for executing given Wasm instructions,
\calli{} for an AL function call with let binding, \replaceframei{} for
replacing a frame, or \replacestorei{} for replacing a store.
% expression
An expression is a variable, number, boolean, AL function name, list, record
(or struct), tuple, tagged tuple, unary or binary operation, data structure
access or update, list or record concatenation, membership check, element
selection, length retrieval, tag check, Wasm context retrieval, Wasm context
kind check, iteration, match relation, or type relation.

@@

  wi = \getendinstr(wc) \qquad
  wi_1 = \getendinstr(wc_1) \quad ... \quad wi_n = \getendinstr(wc_n) \\

@@

@@

  ((\seq{we'}, \seq{wi'}, sto), \algo ~ (\setenv(c', \mu))) \\

@@

Given algorithms $\seq a$, a Wasm state $w$, and a context $c$, executing an
instruction $i$ produces an updated Wasm state and a continuation.
% If
$\ifi ~ (e, i_1^*, i_2^*)${} evaluates $e$ and branches to $\seq i_1$ if the
result is true, or $\seq i_2$ otherwise.
% Either
$\eitheri ~ (i_1^*, i_2^*)${} nondeterministically selects either $i_1^*$ or
$i_2^*$.
% Enter
$\enteri ~ (e_1, e_2)${} evaluates $e_1$, pushing the resulting Wasm context
$wc$ to the interleaved stack.
It then evaluates $e_2$ to obtain the Wasm instruction sequence $wi_1^*$.
Then, the end instructions of the Wasm context $wc$ and the Wasm contexts
$wc_1 ~ ... ~ wc_n$ in the context $c$ are appended to $wi_1^*$ and pushed to
the Wasm instruction stack.
Finally, it changes the continuation to
$\wasm ~ (wc ~ wc_1 ~ ... ~ wc_n, \algo ~ (i^*, \mu, \epsilon, k))${}.
% PushCtx
$\pushctxi ~ e${} evaluates $e$, pushing the resulting Wasm context $wc$ to the
interleaved stack and the context $c$.
% Push
$\pushi ~ e${} evaluates $e$, pushing the resulting value $wv$ to the
interleaved stack.
% PopCtx
$\popctxi ~ e${} pops all Wasm values up to and including a Wasm context $wc$
from the interleaved stack and all Wasm instructions up to and including an end
instruction from the Wasm instruction stack.
It also pops a Wasm context from the context $c$.
Then, it assign the Wasm context $wc$ to $e$.
% Pop
$\popi ~ e${} pops a Wasm value $wv$ from the interleaved stack and assign the
value to $e$.
% PopN
$\popni ~ (e_1, e_2)${} evaluates $e_2$ to obtain a number $n$, pops $n$ Wasm
values from the interleaved stack, and assigns the values to $e_1$.
% PopAll
$\popalli ~ e${} pops all the Wasm values up to, but not including, a
Wasm context from the interleaved stack and assign the values to $e$.
% Let
$\leti ~ (e_1, e_2)${} evaluates $e_2$ and assigns the resulting value to
$e_1$.
% Trap
\trapi{} results in $\ret ~ (\trapv{}, \mt{})$ to terminate the execution.
% ReturnRel
\returnreli{} results in the continuation $k$ in the context $c$, indicating a
return from a relation algorithm.
% ReturnFunc
$\returnfuni ~ e${} evaluates $e$ to $v$, resulting in $\ret ~ (v, k)${} where
$k$ is the continuation in the context $c$.
% Execute
\executei{} evaluates $e$ to obtain a Wasm instruction sequence $wi^*$ and
result in $\exe ~ (wi^*, \algo ~ c)${}.
% Call
$\calli ~ (s_1, s_2, e_1 ~ ... ~ e_n)${} checks if $s_2$ is bound in the
environment.
If it is, it retrieves the function name $s_3$ from the environment $\mu$;
otherwise, it uses $s_2$ as the function name.
It evaluates $\seq e$ to $v^*$, resulting in $\call ~ (s_1, s_{name}, v_1 ~ ...
~ v_n)${} where $s_{name}$ is the function name.
% ReplaceFrame
\replaceframei{} retrieves the current frame $\casev ~ (\text{``Frame"}, v_1
v_2)${} in the Wasm context $w$.
It then evaluates $e$ to $v$, updating the value at location $v_2$ along paths
$p^+$ to $v$.
% ReplaceFrame
\replacestorei{} evaluates $e$ to $v$, updating the value at location $\strv ~
sto$ along paths $p^+$ to v.

@@

      \seq{wi} &\quad\quad \premise{if}\quad ~ \isendinstr(wi) \\

@@

% get_end_algo
  &\getendinstr(wc) =
    \casev ~ (\text{``Exiting"}, \epsilon) &\quad\quad\premise{if}\quad wc = \casev ~ (\text{``Label"}, \seq v)\\
    \casev ~ (\text{``Returning"}, \epsilon) &\quad\quad\premise{if}\quad wc = \casev ~ (\text{``Frame"}, \seq v)
% is_end_instr
  &\isendinstr(wi) =
    true &\quad\quad\premise{if}\quad wi = \casev ~ (\text{``Exiting"}, \epsilon) \quad\lor\quad wi = \casev ~ (\text{``Returning"}, \epsilon)\\
    false &\quad\quad\premise{otherwise}

>>>>

@@

% TODO: Clever way to distinguish jargon rather then \textit
% Formal model
To formally specify the prose specification, we construct a formal model to
describe Wasm control flow.
% Execute
Rather than relying on a program counter, we employ an instruction stack to
represent execution progress.
Execution proceeds by popping an instruction from the stack and performing its
operation.
To avoid confusion with the stack that contains values interleaved with
contexts, we refer to the latter as the \textit{interleaved stack}.
This approach allows us to define the execute operation without introducing a
program counter.

% Jump
We then split two distinct usages of the jump operation: \textit{enter} and
\textit{exit}.
Since Wasm supports structured control flow, the jump operation is used either
for entering or exiting control structures such as a function body and a block
of instructions.
% Enter
We define the enter as the operation of pushing the context associated with the
jump onto the interleaved stack and the instructions within the structure onto
the instruction stack.
Similarly, we define exit as the operation of popping the corresponding context
and instructions.

% State transition
To express the enter and exit operation formally, we model them as state
transitions.
We define a Wasm state as a tuple of the interleaved stack, the instruction
stack, and the store.
For brevity, we omit the store in this discussion.
Let the interleaved stack initially contains $n$ entries $we_1 ~ ... ~ we_n$,
and the instruction stack contains $m$ entries $wi_1 ~ ... ~ wi_m$.
Suppose $wi_1$ is a control instruction that enters a control structure
containing a sequence of k instrucitons $wi_{11} ~ ... ~ wi_{1k}$ with an
associated context $wc$.
The enter operation can be expressed as the following state transition:
\[
(we_1 ~ ... ~ we_n, ~ wi_1 ~ ... ~ wi_m) \quad\leadsto\quad
  (
    wc ~ we_1 ~ ...  ~ we_n, ~
    wi_{11} ~ ... ~ wi_{1k} ~ \textbf{end}_{wc} ~ wi_2 ~ ... ~ wi_m
  )
\]

% End
Note that we introduce an administrative instruction, \textbf{end}, to mark the
end of the structure in the instruction stack.
It models unique behavior described in the prose specification that must take
place when the end of a structure is reached without control transfer.
For example, if a function body executes without concluding with a
\texttt{return} instruction, a behavior that corresponds to the \texttt{return}
is performed.
\cref{fig:exiting-label} illustrates this behavior.
While not a Wasm instruction itself, it is represented in the same way as Wasm
instructions.
Therefore, we formalize this behavior as an administrative instruction,
\textbf{end}.

% Exit
In the same way, the exit operation can be described as a transition of Wasm
state.
Suppose $wi_1$ is a control instruction that exits a control structure, and $i$
values $wv_1 ~ ... wv_i$ are at the top of the interleaved stack, followed by a
context $wc$, and $j$ instructions $wi_1 ~ ... ~ wi_j$ are at the top of the
instruction stack followed by an \textbf{end} instruction.
The exit operation can be represented as the following state transition:
\[
(wv_1 ~ ... ~ wv_i ~ wc ~ we_{i+2} ~ ...  ~ we_n,
  wi_1 ~ ... ~ wi_j ~ \textbf{end}_{wc} ~ wi_{j+2} ~ ..  ~ wi_m)
  \quad\leadsto\quad
  (we_{i+1} ~ ... ~ we_n, wi_{j+1} ~ ... ~ wi_m)
\]
This transition model provides the foundation for the formal definition of AL.

% XXX: HACK
\newpage

\begin{figure}[h]
  \centerline{\includegraphics[width=15cm]{fig/return}}
  \caption[\texttt{return} instruction]{\texttt{return} instruction}
    \label{fig:return}
  \centerline{\includegraphics[width=15cm]{fig/if}}
  \caption[\texttt{if} instruction]{\texttt{if} instruction}
    \label{fig:if}
  \centerline{\includegraphics[width=15cm]{fig/returning}}
  \caption[Behavior for the end a block]{Behavior for the end of a block}
    \label{fig:exiting-label}
\end{figure}

@@

{
\renewcommand{\arraystretch}{0.97}  % Decrease row spacing locally
\begin{align*}
\begin{array}{lcccrlr}
%
% Algorithm
  \text{Algorithm}\quad& A &\ni& a &::=& ~ \rel ~ (s, \seq e, \seq i) ~ | ~ \fun ~ (s, \seq e, \seq i) \\
%
% Instruction
  \text{Instruction}\quad& I &\ni& i &::=& ~ \ifi ~ (e, \seq i, \seq i) &\quad\text{(If)} \\
    &&&& | & ~ \eitheri ~ (\seq i, \seq i) &\quad\text{(Either)} \\
    &&&& | & ~ \enteri ~ (e, e) &\quad\text{(Enter)} \\
    &&&& | & ~ \pushctxi ~ e &\quad\text{(Push Context)} \\
    &&&& | & ~ \pushi ~ e &\quad\text{(Push)} \\
    &&&& | & ~ \exiti ~ &\quad\text{(Exit)} \\
    &&&& | & ~ \popctxi ~ e &\quad\text{(Pop Context)} \\
    &&&& | & ~ \popi ~ e &\quad\text{(Pop)} \\
    &&&& | & ~ \popni ~ (e, e) &\quad\text{(Pop N)} \\
    &&&& | & ~ \popalli ~ e &\quad\text{(Pop All)} \\
    &&&& | & ~ \leti ~ (e, e) &\quad\text{(Let)} \\
    &&&& | & ~ \trapi &\quad\text{(Trap)} \\
    &&&& | & ~ \returnreli &\quad\text{(Return Relation)} \\
    &&&& | & ~ \returnfuni ~ e &\quad\text{(Return Function)} \\
    &&&& | & ~ \executei ~ e &\quad\text{(Execute)} \\
    &&&& | & ~ \calli ~ (s, s, \seq{e}) &\quad\text{(Let Call)} \\
    &&&& | & ~ \replaceframei ~ (p^+, e) &\quad\text{(Replace Frame)} \\
    &&&& | & ~ \replacestorei ~ (p^+, e) &\quad\text{(Replace Store)} \\
%
% Expression
  \text{Expression}\quad& E &\ni& e &::=& ~ \vare ~ s &\quad\text{(Variable)} \\
    &&&& | & ~ \nume ~ n &\quad\text{(Number)} \\
    &&&& | & ~ \boole ~ b &\quad\text{(Boolean)} \\
    &&&& | & ~ \fnamee ~ s &\quad\text{(Function Name)} \\
    &&&& | & ~ \liste ~ \seq e &\quad\text{(List)} \\
    &&&& | & ~ \stre ~ \seq{(s, e)} &\quad\text{(Record)} \\
    &&&& | & ~ \tupe ~ \seq e &\quad\text{(Tuple)} \\
    &&&& | & ~ \casee ~ (s, \seq e) &\quad\text{(Tagged Tuple)} \\
    &&&& | & ~ \une ~ (unop, e) &\quad\text{(Unary Operation)} \\
    &&&& | & ~ \bine ~ (binop, e, e) &\quad\text{(Binary Operation)} \\
    &&&& | & ~ \acce ~ (e, p) &\quad\text{(Access)} \\
    &&&& | & ~ \upde ~ (e, p^+, e) &\quad\text{(Update)} \\
    &&&& | & ~ \cate ~ (e, e) &\quad\text{(Concatenation)} \\
    &&&& | & ~ \compe ~ (e, e) &\quad\text{(Composition)} \\
    &&&& | & ~ \meme ~ (e, e) &\quad\text{(Membership)} \\
    &&&& | & ~ \choosee ~ e &\quad\text{(Choose)} \\
    &&&& | & ~ \lene ~ e &\quad\text{(Length)} \\
    &&&& | & ~ \iscaseofe ~ (e, s) &\quad\text{(Check Tag)} \\
    &&&& | & ~ \getcurctxe  &\quad\text{(Get Current Context)} \\
    &&&& | & ~ \ctxkinde ~ s &\quad\text{(Context Kind)} \\
    &&&& | & ~ \itere ~ (e, iter, \seq{s}) &\quad\text{(Iteration)} \\
    &&&& | & ~ \matche ~ (e, e) &\quad\text{(Match)} \\
    &&&& | & ~ \hastypee ~ (e, s) &\quad\text{(Has Type)} \\
\end{array}
\end{align*}
}

@@

% algorithm
An algorithm is either an AL relation or an AL function, corresponding to the
relation and the function definitions in the DSL.
% instruction
An AL instruction is \ifi{} for conditionally choosing a branch, \eitheri{} for
nondeterministically choosing a branch, \enteri{} for entering a control
structure, \pushctxi{} for pushing a Wasm context, \pushi{} for pushing a Wasm
value, \exiti{} for exiting a control structure, \popctxi{} for popping a Wasm
context, \popi{} for popping a Wasm value, \popni{} for popping $n$ Wasm
values, \popalli{} for popping all Wasm values within a Wasm context, \leti{}
for let binding, \trapi{} for trapping, \returnreli{} for returning from an AL
relation, \returnfuni{} for returning from an AL function, \executei{} for
executing given Wasm instructions, \calli{} for an AL function call with let
binding, \replaceframei{} for replacing a frame, or \replacestorei{} for
replacing a store.
% expression
An expression is a variable, number, boolean, AL function name, list, record
(or struct), tuple, tagged tuple, unary or binary operation, data structure
access or update, list or record concatenation, membership check, element
selection, length retrieval, tag check, Wasm context retrieval, Wasm context
kind check, iteration, match relation, or type relation.

@@

  wi = \casev ~ (\text{"End"}, wc) \qquad
  wi_1 = \casev ~ (\text{"End"}, wc_1) \quad ... \quad wi_n = \casev ~ (\text{"End"}, wc_n) \\

@@

% Exit
  \seq{a}, w, c \vdash \exiti
  ((\seq{we'}, \seq{wi'}, sto), \algo ~ c') \\

@@

  ((\seq{wv} ~ \seq{we'}, \seq{wi}, sto), \algo ~ (\setenv(c', \mu))) \\

@@

Given algorithms $\seq a$, a Wasm state $w$, and a context $c$, executing an
instruction $i$ produces an updated Wasm state and a continuation.
% If
$\ifi ~ (e, i_1^*, i_2^*)${} evaluates $e$ and branches to $\seq i_1$ if the
result is true, or $\seq i_2$ otherwise.
% Either
$\eitheri ~ (i_1^*, i_2^*)${} nondeterministically selects either $i_1^*$ or
$i_2^*$.
% Enter
$\enteri ~ (e_1, e_2)${} evaluates $e_1$, pushing the resulting Wasm context
$wc$ to the interleaved stack.
It then evaluates $e_2$ to obtain the Wasm instruction sequence $wi_1^*$.
Then, the end instructions of the Wasm context $wc$ and the Wasm contexts
$wc_1 ~ ... ~ wc_n$ in the context $c$ are appended to $wi_1^*$ and pushed to
the Wasm instruction stack.
Finally, it changes the continuation to
$\wasm ~ (wc ~ wc_1 ~ ... ~ wc_n, \algo ~ (i^*, \mu, \epsilon, k))${}.
% PushCtx
$\pushctxi ~ e${} evaluates $e$, pushing the resulting Wasm context $wc$ to the
interleaved stack and the context $c$.
% Push
$\pushi ~ e${} evaluates $e$, pushing the resulting value $wv$ to the
interleaved stack.
% Exit
$\exiti${} pops all Wasm values up to and including a Wasm context $wc$ from
the interleaved stack and all Wasm instructions up to and including an end
instruction from the Wasm instruction stack.
It also pops a Wasm context from the context $c$.
% PopCtx
$\popctxi ~ e${} pops a Wasm context $wc$ from the interleaved stack.
It also pops a Wasm context from the context $c$.
Then, it assign the Wasm context $wc$ to $e$.
% Pop
$\popi ~ e${} pops a Wasm value $wv$ from the interleaved stack and assign the
value to $e$.
% PopN
$\popni ~ (e_1, e_2)${} evaluates $e_2$ to obtain a number $n$, pops $n$ Wasm
values from the interleaved stack, and assigns the values to $e_1$.
% PopAll
$\popalli ~ e${} pops all the Wasm values up to, but not including, a
Wasm context from the interleaved stack and assign the values to $e$.
% Let
$\leti ~ (e_1, e_2)${} evaluates $e_2$ and assigns the resulting value to
$e_1$.
% Trap
\trapi{} results in $\ret ~ (\trapv{}, \mt{})$ to terminate the execution.
% ReturnRel
\returnreli{} results in the continuation $k$ in the context $c$, indicating a
return from a relation algorithm.
% ReturnFunc
$\returnfuni ~ e${} evaluates $e$ to $v$, resulting in $\ret ~ (v, k)${} where
$k$ is the continuation in the context $c$.
% Execute
\executei{} evaluates $e$ to obtain a Wasm instruction sequence $wi^*$ and
result in $\exe ~ (wi^*, \algo ~ c)${}.
% Call
$\calli ~ (s_1, s_2, e_1 ~ ... ~ e_n)${} checks if $s_2$ is bound in the
environment.
If it is, it retrieves the function name $s_3$ from the environment $\mu$;
otherwise, it uses $s_2$ as the function name.
It evaluates $\seq e$ to $v^*$, resulting in $\call ~ (s_1, s_{name}, v_1 ~ ...
~ v_n)${} where $s_{name}$ is the function name.
% ReplaceFrame
\replaceframei{} retrieves the current frame $\casev ~ (\text{``Frame"}, v_1
v_2)${} in the Wasm context $w$.
It then evaluates $e$ to $v$, updating the value at location $v_2$ along paths
$p^+$ to $v$.
% ReplaceFrame
\replacestorei{} evaluates $e$ to $v$, updating the value at location $\strv ~
sto$ along paths $p^+$ to v.

@@

      \seq{wi} &\quad\quad \premise{if}\quad ~ wi = \casev ~ (\text{"End"}, wc) \\

@@
